Modelling BCG vaccination in the UK

### 2019-08-05 rmds/02-background.Rmd
update word count

## Wordcount: 3501
##packages
##Install via 
##Dev Version:: devtools::install_github("seabbs/tbinenglanddataclean")
library(tbinenglanddataclean)
library(prettypublisher)
library(tidyverse)
library(kableExtra)
library(pander)
library(getTBinR)
##Resources path
resources_path  <- file.path("chapters", "background")
```

>>>>

## Wordcount: 3675
##packages
##Install via 
##Dev Version:: devtools::install_github("seabbs/tbinenglanddataclean")
library(tbinenglanddataclean)
library(prettypublisher)
library(tidyverse)
library(kableExtra)
library(pander)
library(getTBinR)
##Resources path
resources_path  <- file.path("chapters", "background")
```

### 2019-08-05 rmds/03-getTBinR.Rmd
update word count

```{r gettbinr-setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, dpi = 320, cache = TRUE,
                      fig.width = 8, fig.height = 8,
                      out.width = "80%", fig.align = 'center')
## Wordcount: 1796
##packages
## Install via 
## CRAN: install.packages("getTBinR")
## Dev Version:: devtools::install_github("seabbs/getTBinR", update = TRUE)
library(getTBinR)
library(tidyverse)
## Resources path
resources_path <- file.path("chapters", "getTBinR")
```

>>>>

```{r gettbinr-setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, dpi = 320, cache = TRUE,
                      fig.width = 8, fig.height = 8,
                      out.width = "80%", fig.align = 'center')
## Wordcount:2133
##packages
## Install via 
## CRAN: install.packages("getTBinR")
## Dev Version:: devtools::install_github("seabbs/getTBinR", update = TRUE)
library(getTBinR)
library(tidyverse)
## Resources path
resources_path <- file.path("chapters", "getTBinR")
```

### 2019-08-05 rmds/04-tb-epi-england.Rmd
update word count

```{r tb-epi-setup, include=FALSE}
regen_results <- FALSE
knitr::opts_chunk$set(echo = FALSE, warnings = FALSE,
                      fig.width = 8, fig.height = 8,
                      out.width = "80%", fig.align = 'center')
##Wordcount: 8497
```

>>>>

```{r tb-epi-setup, include=FALSE}
regen_results <- FALSE
knitr::opts_chunk$set(echo = FALSE, warnings = FALSE,
                      fig.width = 8, fig.height = 8,
                      out.width = "80%", fig.align = 'center')
##Wordcount: 8577
```

### 2019-08-05 rmds/05-evidence-policy-change.Rmd
update word count

## Read formated results
## See https://github.com/seabbs/AssessBCGPolicyChange/blob/master/vignettes/paper.Rmd
## for code required to reproduce 
## Chapter is an edited version of the orginal reproducible document.
## Original results found at: https://github.com/seabbs/AssessBCGPolicyChange/blob/master/vignettes/results/paper
## Original figures found at: https://github.com/seabbs/AssessBCGPolicyChange/blob/master/docs/articles/paper_files/figure-html
##Wordcount: 4249

>>>>

## Read formated results
## See https://github.com/seabbs/AssessBCGPolicyChange/blob/master/vignettes/paper.Rmd
## for code required to reproduce 
## Chapter is an edited version of the orginal reproducible document.
## Original results found at: https://github.com/seabbs/AssessBCGPolicyChange/blob/master/vignettes/results/paper
## Original figures found at: https://github.com/seabbs/AssessBCGPolicyChange/blob/master/docs/articles/paper_files/figure-html
##Wordcount: 4274

### 2019-08-05 rmds/06-tb-bcg-improv-outcomes.Rmd
update word count

```{r setup, include = FALSE, eval = TRUE}
## Word count: 3869
## Packages
library(tidyverse)
library(knitr)
library(kableExtra)
library(pander)
library(prettypublisher)

>>>>

```{r 06-setup, include = FALSE, eval = TRUE}
## Word count: 3892
## Packages
library(tidyverse)
library(knitr)
library(kableExtra)
library(pander)
library(prettypublisher)

### 2019-08-05 rmds/08-model-development.Rmd
update word count

## Wordcount: 10220
##packages
library(tidyverse)
library(kableExtra)
library(pander)
## Resources path
resources_path <- file.path("chapters", "model-development")

>>>>

## Wordcount: 11090
##packages
library(tidyverse)
library(kableExtra)
library(pander)
## Resources path
resources_path <- file.path("chapters", "model-development")

### 2019-08-05 rmds/09-model-fitting.Rmd
update word count

## Wordcount: 5501
##packages
library(tidyverse)
library(purrr)
library(kableExtra)
library(pander)
library(fs)
## Resources path
resources_path <- file.path("chapters", "model-fitting")

>>>>

## Wordcount: 9286
##packages
library(tidyverse)
library(purrr)
library(kableExtra)
library(pander)
library(fs)
## Resources path
resources_path <- file.path("chapters", "model-fitting")

### 2019-08-05 rmds/index.Rmd
update word count

---
author: 'Samuel Abbott'
date: 'August 2019'
division: 'Bristol Medical School\: Population Health Sciences'
advisor: 'Ellen Brooks Pollock'
altadvisor: 'Hannah Christensen'
department: 'Faculty of Health Sciences'
title: 'Modelling BCG vaccination in the UK'
subtitle: 'What is the impact of changing policy?'
wordcount: "41,218"
knit: "bookdown::render_book"
site: "bookdown::bookdown_site"
always_allow_html: yes
output: 
  ##Thesis can only be fully built for pdf using the makefile
  #thesisdown::thesis_pdf: default
  thesisdown::thesis_gitbook: default
  #thesisdown::thesis_word: default
  #thesisdown::thesis_epub: default
bibliography: ["bib/thesis.bib"]
#Download your specific bibliography database file and refer to it in the line above.
link-citations: yes
colorlinks: yes
csl: ["csl/bmj.csl"]
#Download your specific csl file and refer to it in the line above.
lot: true
lof: true
space_between_paragraphs: true
#Delete the # at the beginning of the previous line if you'd like
#to have a blank new line between each paragraph
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}

>>>>

---
author: 'Samuel Abbott'
date: 'August 2019'
division: 'Bristol Medical School\: Population Health Sciences'
advisor: 'Ellen Brooks Pollock'
altadvisor: 'Hannah Christensen'
department: 'Faculty of Health Sciences'
title: 'Modelling BCG vaccination in the UK'
subtitle: 'What is the impact of changing policy?'
wordcount: "54,957"
knit: "bookdown::render_book"
site: "bookdown::bookdown_site"
always_allow_html: yes
output: 
  ##Thesis can only be fully built for pdf using the makefile
  #thesisdown::thesis_pdf: default
  thesisdown::thesis_gitbook: default
  #thesisdown::thesis_word: default
  #thesisdown::thesis_epub: default
bibliography: ["bib/thesis.bib"]
#Download your specific bibliography database file and refer to it in the line above.
link-citations: yes
colorlinks: yes
csl: ["csl/bmj.csl"]
#Download your specific csl file and refer to it in the line above.
lot: true
lof: true
space_between_paragraphs: true
#Delete the # at the beginning of the previous line if you'd like
#to have a blank new line between each paragraph
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
